Hypernetwork-PPO for Continual Reinforcement Learning

### 2022-09-28 thesis/paper/main.tex
revisions on paper for NeurIPS workshop submission

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}

@@

% Macros for comments
\newcommand{\comment}[1]{}
\newcommand{\todo}[1] {\comment{{\color{red} TODO: #1}}}             % TODO
\newcommand{\ps}[1] {\comment{{\color {purple} PS: #1}}}             % Comments by Philemon
\newcommand{\sa}[1] {\comment{{\color{cyan} SA: #1}}}                % Comments by Sayantan
\newcommand{\jh}[1] {\comment{{\color{RawSienna} JH: #1}}}           % Comments by Jakob
\newcommand{\as}[1] {\comment{{\color{orange} AS: #1}}}              % Comments by Antonio

\begin{document}
\maketitle
\sa{We need to think about the title. At present this is far too generic.}

\begin{abstract}
\jh{Recently someone mentioned the following structure for the abstract: 1/3 introduction, 1/3 problem, 1/3 solution.}
Continually learning new capabilities in different environments, and being able to solve multiple complex tasks is of great importance for many robotics applications. Modern reinforcement learning algorithms such as Proximal Policy Optimization can successfully handle surprisingly difficult tasks, but are generally not suited for multi-task or continual learning. Hypernetworks are a promising approach to avoiding catastrophic forgetting, and have previously been used successfully in model-based continual RL. We propose \texttt{HN-PPO}, a continual RL method employing a hypernetwork to learn multiple policies in a continual manner using PPO. We demonstrate our method on DoorGym, and show that it is suitable for solving tasks involving complex dynamics such as door opening, while effectively protecting against catastrophic forgetting. 
\end{abstract}

\section{Introduction}
\label{chap:intro}
Adapting to changing environments is a crucial and desirable ability for many robot systems. Advances in reinforcement learning (RL) such as Proximal Policy Optimization (PPO) \citep{ppo} or Soft Actor-Critic (SAC) \citep{sac} have enabled simulated robots to excel at solving complex continuous control tasks such as moving a stick figure and humanoid walking \citep{ppo}. 
\sa{PPO and SAC are both algorithms for continuous action spaces, while Atari games have a discrete action space. Change this to a suitable example.}
However, the resulting agents generally can only solve one narrowly defined task. When a new task is learned by fine-tuning the existing model 
\as{is "fine-tuning" the right word?, maybe"adjustment"?}\jh{I think fine-tuning is the right word, but fine-tuning is not very common in RL; I mean the continual-RL field is very young/small; So I think you should add a little bit of text that smooths the transition and explains that you want to extend or re-use the previously learned things. Maybe the problem is that here you basically introduce continual learning without mentioning continual learning.}
, the ability to solve the old task is often greatly diminished or completely lost - a phenomenon known as \textit{catastrophic forgetting}\sa{Cite the Parisi CL review paper}. Although a well-known problem \citep{MCCLOSKEY1989109}, catastrophic forgetting in sequential multi-task settings is still a major limitation for machine learning systems. This is in stark contrast to human learning, which very rarely exhibits forgetting when learning a new task \citep{parisiClReview}.

A variety of \textit{continual learning} (CL) methods have been proposed to overcome this limitation. In a CL setting, multiple tasks are to be learned sequentially, while retaining or even improving knowledge about past tasks \citep{towardsCRL}. A naive approach towards this goal would be recording all previous experience of an agent, and replaying the recorded experience to a new agent when training new tasks. 
\sa{For RL there is no training data as in supervised learning. What can be stored are the (S,A,R,S') tuples in a replay buffer which can then be utilized by an offline RL algorithm. Is this what you wanted to imply?}
However, this method requires vast amounts of memory to store experiences, and thus does not scale well to a large number of tasks. Therefore CL desiderata often assume that previous experience will not be available when training new tasks \citep{lwf}.

\sa{This (or the end of this paragraph) is a good place to mention that previous work has used HN for model based RL, and we show that HN is a good candidate for continual RL for a state-of-the-art model-free algorithm as well. You should also mention the other differences with the MBRL paper (e.g. more types of doors, reporting of the door opening rate, etc.}
Hypernetworks have been previously proposed as a promising method \citep{CLHypernetworks} for supervised continual learning. More recently, task-conditioned hypernetworks have also been employed in a model-based continual RL setting using the cross-entropy method (CEM) \citep{MBRLHypernetworks}.

%\jh{How about a "Contribution" paragraph heading such as this:}

@@

%\jh{$<-$}
%\jh{Basically we're proposing model-free continual-learning \textbf{policies} using hyper-networks, right? 
%So basically, we propose to learn policies that can perform multiple task, and learn those policies in a continual-learning fashion; And we use hyper-networks for that. This sets us apart from previous %work \citet{MBRLHypernetworks} because they used continual learning to learn a Multi-Task? Transition model on which they performed model predictive control using CEM. }
In this paper, we expand upon the work of \citet{MBRLHypernetworks}; evaluating the use of task-conditioned hypernetworks in \textit{model-free} continual RL. To this end, we propose a hypernetwork-based implementation of PPO (\texttt{HN-PPO}), a state-of-the-art online RL algorithm \as{I would remove the "simple-to-implement", do not see the relevance}. We show that \texttt{HN-PPO} can overcome catastrophic forgetting experienced by baseline PPO agents. In a single-task setting, \texttt{HN-PPO} has comparable success rates to what baseline PPO can achieve. Further, we conduct an ablation study confirming the importance of regularizing the hypernetwork on previous tasks in order to avoid catastrophic forgetting.\\
As \citet{MBRLHypernetworks}, we use the DoorGym environment \citep{doorgym} in our experiments to demonstrate our method. This environment was chosen for its relevance to real-world robotics, where door opening is a highly relevant skill for autonomous mobile robots. Door opening is a well-suited scenario for continual RL, since a robot may encounter many different kinds of doors during its life. The clear separation between different kinds of doors also fits well with the \textit{task-incremental} \cite{threescenarios} CL scenario, where the task identity is clearly defined, and known at training and evaluation time. Our main contributions are:
\begin{itemize}
    \item A model-free continual RL algorithm, \texttt{HN-PPO}, using hypernetworks to learn a multi-task policy
    \item An evaluation of CL performance in DoorGym using the door opening success rate as the main performance indicator.
\end{itemize}

%\jh{I would use bullet points for the contributions; and if we provide a better evaluation than that might also be a contribution;}

%\sa{Right now, the introduction is too short and a few other things need to be mentioned, such as the motivation behind this work (or why this is useful), a brief overview of our experimental setup (why %the doors environment is a good choice), a summary of the main contributions/findings, etc. It is useful for the reader if the doors environment is mentioned here, otherwise it suddenly jumps out of %nothing.

@@

\jh{I don't know if this contradicts what SA and AS but what I would do is to state the area of this work very briefly in the introduction (you are already doing that) and then list the contributions. And then basically start from adam and eve (in terms of RL, but very briefly) i.e. DQN -> Continuous Spaces -> SAC, PPO -> Continual Learning (what is it) -> CL other methods; Mostly you are already doing that. But for example in the paragraph "a varienty of contiual learning".. you describe continual learning more like you would in related work (IMO). 
The reason for that is that the reviewers often do also not know a lot about the very specific field you are working on.
An example of this would be \url{https://arxiv.org/pdf/2206.03787.pdf} -- but this is also a personal taste thing.
SA-CHECK}
\section{Related Work} %\as{Fuse with the previous section and use "Related Work" as its title}
\paragraph{CL strategies} The many strategies for retaining previously learned knowledge, and thus alleviating the catastrophic forgetting problem, can be broadly categorized into four approaches according to \citet{threescenarios2}: Context-specific components, regularization, replay, and template methods. The latter is however most relevant for continual classification problems, and less so for unsupervised RL settings. A similar classification has also been made in a review of CL methods by \citet{towardsCRL}.\\
Context-specificity methods add parts to the network that are specific for each task, i.e. are only trained on a single task. Such methods include context-specific gating \citep{xdg}, which creates context-specificity by randomly excluding a subset of neurons from the network for each task, or progressive neural networks \citep{pnn}, in which a completely new set of parameters is trained for each task, and information is transferred from previous tasks via lateral connections between layers.\\
Regularization can be applied at two levels to avoid catastrophic forgetting: In \textit{parameter} regularization, the objective is to minimize the changes of parameters which are important for previously learned tasks. The main challenge of parameter regularization is finding which parameters are most important to retain previous knowledge: \citet{ewc} use the Fisher information matrix to estimate parameter importance, and \citet{synapticintelligence} propose an online-learned importance measure in their \textit{synaptic intelligence} algorithm. Alternatively, regularization can be applied at the \textit{functional} level. Herein, the output of the network is encouraged to stay close to a target for a set of anchor points. Anchor points could be chosen from previous experience, or if it is undesired to store this data, a knowledge distillation loss can be used for functional regularization, as in \citet{lwf}. They propose a hybrid of functional regularization and parameter storage: \as{ok, and?. Make sure that what you write is informative} Firstly, the network has a context-specific output layer, and regularization is applied between the new and previous outputs of the context-specific components of previous tasks, but using input data from the current task.\\
Finally, replay methods store experience from previous tasks in a buffer, and agents consequently revisit the recorded experience when training for new tasks. The policy is then jointly optimized on the current and replayed experience. Even though conceptually simple, replay suffers from bad scalability over many tasks, since large amounts of memory are required to store all past experience. An approach to improve scalability is to train a generative alongside the policy model, and then sample from this model to obtain pseudo-data to revisit \citep{generativeReplay}.

\sa{I'm not sure we need to write about LwF. But in any case, it will be beneficial to include an overview of continual RL methods (or those specifically applied to robotics). Check this paper for a review of such methods: \url{https://arxiv.org/pdf/2012.13490.pdf}. I also think that we need a little more content here.}

\paragraph{DoorGym} %\as{Again???. As before, fuse with previous section}
The DoorGym \citep{doorgym} environment is a robot simulation based on OpenAI Gym \citep{gym}, where robot arms aim to open a door. Robots are controlled via a set of continuous input variables modeling joint torque (or torque and force on the end effector in case of \texttt{floating} robots). Different types of tasks are modeled through the door knob style (\texttt{pull}, \texttt{lever} or \texttt{round}) as well as the location of the hinge (\texttt{right} or \texttt{left}) and the opening direction (\texttt{pull} or \texttt{push}). Environments within a task domain have a multitude of randomized features, such as the location of the handle on the door, the exact shape of the handle, or the spring force on the lever and hinge.
The original authors of the DoorGym environment \cite{doorgym} provide a baseline PPO and SAC agent for the \texttt{pull} and \texttt{lever} doors. It is demonstrated that PPO and SAC are in principle suitable to solve the door opening tasks, both in their ground configuration, and with added noise. We use their set of hyperparameters for the PPO agent for our experiments using PPO, as well as as a starting point for finding hyperparameters for HN-PPO. Of note, the authors did not make any attempt at a continual RL agent, nor was the DoorGym environment designed specifically for continual learning.\\
\citet{MBRLHypernetworks} explores continual RL in DoorGym using the model-based cross-entropy method (CEM). \textit{HyperCRL} on the DoorGym environment. Herein, it is shown that catastrophic forgetting occurs between different DoorGym tasks with traditional RL methods, and task-conditioned hypernetworks are established as a promising method to alleviate this. However, in their paper, it was not shown that the tasks could be completely solved, as they only reported normalized episode rewards, not success rates.

\section{Background}
\as{There should be here an introductory sentence on the areas you are going to review below and why. There has to be a link between them.}
Our proposed method uses PPO \citep{ppo} to continually learn policies for different door-opening tasks of the DoorGym environment \citep{doorgym}. A hypernetwork \cite{CLHypernetworks} architecture is used to prevent catastrophic forgetting.

@@

To preserve previously learned skills, regularization is applied at the meta-level: At the beginning of training a new task, the outputs $\Theta_t$ of the hypernetwork are recorded for each previous task embedding $t$ \citep{CLHypernetworks}. Since this output completely defines the target network for a each task, keeping the $\Theta_t$ constant during training of a new task will guarantee preservation of the learned dynamics. We hence apply an $L2$ penalty on changes of the hypernetwork's output:

@@

Because the update routine requires passing all previous task embeddings through the hypernetwork to calculate the $\Theta_{t,new}$, the computational expense of a training step increases $\mathcal{O}(n)$ with respect to the number of tasks. Importantly though, the model size stays nearly constant\jh{nearly constant is a bit contradictory, no? Maybe you can be more specific by how much it grows.}. Only a low-dimensional embedding vector is added for each task, fulfilling the CL desideratum of not explicitly accumulating previous experience.

\paragraph{Proximal Policy Optimization}
PPO is a policy gradient method using a \textit{clipped surrogate objective}. A policy is optimized by estimating its gradient, and conducting gradient ascent steps to maximize the reward. The gradient is estimated by differentiating the objective function
\begin{equation}
    L_t(\theta) = \mathbb{E}_t\left[\frac{\pi_\theta(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)}\hat{A}_t\right]
\end{equation}
with advantage $\hat{A}_t$, and a probabilistic policy $\pi_{\theta}(a_t|s_t)$. In PPO, this objective is constrained by clipping excessively large changes in probability ratio:
\begin{equation}
\label{ppo-clip}
    L^{clip}_t(\theta)  = \mathbb{E}_t \left[min\left(\frac{\pi_\theta(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)}\hat{A}_t, clip\left(\frac{\pi_\theta(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)}, 1+\epsilon,1-\epsilon \right)\hat{A}_t\right)\right] 
\end{equation}
\citep{ppo}. $\epsilon$ is a hyperparameter and defines the allowable change of the policy. \as{There are some parameters still not defined, like $\pi_\theta$, make sure they all clear what they are}. This improves the policy stability by removing big changes in the probability ratios of the old and new policies during a training step. It is conceptually similar to trust-region policy optimization \cite{trpo}, but is easier to implement, since it omits the KL-divergence based constraint in trust-region policy optimization \as{I think you are abusing the use of acronyms, if you plan to use them less than 5 times, do not use the acronym}.

Additionally to the action objective in Eq. \ref{ppo-clip}, we use a trainable value estimator (called a "critic network") as proposed by \citet{gae} to introduce a value loss term $L^{vf}$. An entropy bonus $S$ is also added to incentivize exploration of the parameter space. The complete objective function thus has 3 parts, with value coefficient $c_v$ and entropy coefficient $c_e$ being hyperparameters.
\begin{equation}
\label{ppo-actorcritic}
    L^{total}_t(\theta) = L^{clip}_t(\theta)+ c_vL^{vf}_t(\theta)+c_eS_{\pi_\theta}(s_t)
\end{equation}

\section{Method}
We extend the existing implementation of PPO in DoorGym to use a hypernetwork to generate the weights of the policy network. Two variants of HN-PPO were implemented: A straightforward implementation (\texttt{HN-PPO}) which places both the actor and critic networks' parameters under the control of the hypernetwork, and a modified variant that only generates the actor network via a hypernetwork and uses an ordinary MLP as the critic (\texttt{HN-PPO+fc}). In the latter variant, the critic is re-initialized for each new task seen by the agent (cf. Appendix \ref{chap:architecture} for details). Because the critic is only used during training, it does not influence the policy at evaluation time, nor is it strictly required to remember multiple dynamics. However, forward transfer characteristics could still benefit learning of new tasks.\\
The PyTorch hypernetwork implementation used in our experiments is from \cite{auddyHollensteinClfd} and was used without modifications.

\subsection{Environment \as{I think what you wrote about DoorGym should go here, otherwise it is way too many places.}}
\sa{Add a subsection for the RL environment and describe here the details of the RL setup and tasks, including any modifications that you made to the default door-gym and the reasons for such modifications. This needs to be connected to the content about door-gym in the background section. So, in the background, you can describe the default door-gym environment and in this section you can describe your specific tasks and modifications.}
In our experiments, we used an unmodified DoorGym \cite{doorgym} environment with the \texttt{blue-floatinghook} robot. This robot type was chosen due to both its simplicity and the good baseline performance on \texttt{pull} and \texttt{lever} doors. The robot resembles a hand with a hook for fingers, and is freely floating in 3D space. It has a 6D continuous input space, with three inputs controlling force in x/y/z direction, and three inputs controlling yaw/pitch/roll torque. None of the noise or vision features of DoorGym were used in our setup, i.e. observations are noise-free and directly derived from the environment simulation. We use the same 6-task sequence laid out in Tab. \ref{tab:tasksequence} for all continual learning experiments. CL agents were sequentially trained on each environment. %Fig. \ref{fig:door-examples} provides example images of the robot interacting with some of the door environments.
\sa{Some example images would be nice to have.}

>>>>

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}

@@

% Macros for comments
%\newcommand{\comment}[1]{} 
\newcommand{\comment}[1]{{#1}}
\newcommand{\todo}[1] {\comment{{\color{red} TODO: #1}}}             % TODO
\newcommand{\ps}[1] {\comment{{\color {purple} PS: #1}}}             % Comments by Philemon
\newcommand{\sa}[1] {\comment{{\color{cyan} SA: #1}}}                % Comments by Sayantan
\newcommand{\jh}[1] {\comment{{\color{RawSienna} JH: #1}}}           % Comments by Jakob
\newcommand{\as}[1] {\comment{{\color{orange} AS: #1}}}              % Comments by Antonio

\newcommand{\commentOLD}[1]{} 
%\newcommand{\commentOLD}[1]{{#1}}
\newcommand{\psOLD}[1] {\commentOLD{{\color {purple} PS: #1}}}             % Comments by Philemon
\newcommand{\saOLD}[1] {\commentOLD{{\color{cyan} SA: #1}}}                % Comments by Sayantan
\newcommand{\jhOLD}[1] {\commentOLD{{\color{RawSienna} JH: #1}}}           % Comments by Jakob
\newcommand{\asOLD}[1] {\commentOLD{{\color{orange} AS: #1}}}              % Comments by Antonio

\begin{document}
\maketitle
\saOLD{We need to think about the title. At present this is far too generic.}

\begin{abstract}
\jhOLD{Recently someone mentioned the following structure for the abstract: 1/3 introduction, 1/3 problem, 1/3 solution.}
Continually learning new capabilities in different environments, and being able to solve multiple complex tasks is of great importance for many robotics applications. Modern reinforcement learning algorithms such as Proximal Policy Optimization can successfully handle surprisingly difficult tasks, but are generally not suited for multi-task or continual learning. Hypernetworks are a promising approach for avoiding catastrophic forgetting, and have previously been used successfully for continual model-learning in model-based RL. We propose \texttt{HN-PPO}, a continual model-free RL method employing a hypernetwork to learn multiple policies in a continual manner using PPO. We demonstrate our method on DoorGym, and show that it is suitable for solving tasks involving complex dynamics such as door opening, while effectively protecting against catastrophic forgetting. 
\end{abstract}

\section{Introduction}
\label{chap:intro}
Adapting to changing environments is a crucial and desirable ability for many robot systems. Advances in reinforcement learning (RL) such as Proximal Policy Optimization (PPO) \citep{ppo} or Soft Actor-Critic (SAC) \citep{sac} have enabled simulated robots to excel at solving complex continuous control tasks such as moving a stick figure and humanoid walking \citep{ppo}. 
\saOLD{PPO and SAC are both algorithms for continuous action spaces, while Atari games have a discrete action space. Change this to a suitable example.}
However, the resulting agents generally can only solve one narrowly defined task. When a new task is learned by fine-tuning the existing model 
\asOLD{is "fine-tuning" the right word?, maybe"adjustment"?}\jhOLD{I think fine-tuning is the right word, but fine-tuning is not very common in RL; I mean the continual-RL field is very young/small; So I think you should add a little bit of text that smooths the transition and explains that you want to extend or re-use the previously learned things. Maybe the problem is that here you basically introduce continual learning without mentioning continual learning.}
, the ability to solve the old task is often greatly diminished or completely lost - a phenomenon known as \textit{catastrophic forgetting}\saOLD{Cite the Parisi CL review paper}. Although a well-known problem \citep{MCCLOSKEY1989109}, catastrophic forgetting in sequential multi-task settings is still a major limitation for machine learning systems. This is in stark contrast to human learning, which very rarely exhibits forgetting when learning a new task \citep{parisiClReview}.

A variety of \textit{continual learning} (CL) methods have been proposed to overcome this limitation. In a CL setting, multiple tasks are to be learned sequentially, while retaining or even improving knowledge about past tasks \citep{towardsCRL}. A naive approach towards this goal would be recording all previous experience of an agent, and replaying the recorded experience to a new agent when training new tasks. 
\saOLD{For RL there is no training data as in supervised learning. What can be stored are the (S,A,R,S') tuples in a replay buffer which can then be utilized by an offline RL algorithm. Is this what you wanted to imply?}
However, this method requires vast amounts of memory to store experiences, and thus does not scale well to a large number of tasks. Therefore CL desiderata often assume that previous experience will not be available when training new tasks \citep{lwf}.

\saOLD{This (or the end of this paragraph) is a good place to mention that previous work has used HN for model based RL, and we show that HN is a good candidate for continual RL for a state-of-the-art model-free algorithm as well. You should also mention the other differences with the MBRL paper (e.g. more types of doors, reporting of the door opening rate, etc.}
Hypernetworks have been previously proposed as a promising method \citep{CLHypernetworks} for supervised continual learning. More recently, task-conditioned hypernetworks have also been employed in a model-based continual RL setting using the cross-entropy method (CEM) \citep{MBRLHypernetworks}.

%\jhOLD{How about a "Contribution" paragraph heading such as this:}

@@

%\jhOLD{$<-$}
%\jhOLD{Basically we're proposing model-free continual-learning \textbf{policies} using hyper-networks, right? 
%So basically, we propose to learn policies that can perform multiple task, and learn those policies in a continual-learning fashion; And we use hyper-networks for that. This sets us apart from previous %work \citet{MBRLHypernetworks} because they used continual learning to learn a Multi-Task? Transition model on which they performed model predictive control using CEM. }
In this paper, we expand upon the work of \citet{MBRLHypernetworks}; evaluating the use of task-conditioned hypernetworks in \textit{model-free} continual RL. To this end, we propose a hypernetwork-based implementation of PPO (\texttt{HN-PPO}), a state-of-the-art online RL algorithm \asOLD{I would remove the "simple-to-implement", do not see the relevance}. 
%We show that \texttt{HN-PPO} can overcome catastrophic forgetting experienced by baseline PPO agents. In a single-task setting, \texttt{HN-PPO} has comparable success rates to what baseline PPO can achieve. 
%\sa{I changed the next sentence, since "single task setting" was a bit unclear.}
% SA start
We show that \texttt{HN-PPO} performs comparably to baseline PPO for learning single tasks, but unlike baseline PPO, it is also able to overcome catastrophic forgetting while learning a sequence of tasks.
% SA end
Further, we conduct an ablation study confirming the importance of regularizing the hypernetwork on previous tasks in order to avoid catastrophic forgetting.

Similar to \citet{MBRLHypernetworks}, we use the DoorGym environment \citep{doorgym} in our experiments to demonstrate our method. This environment was chosen for its relevance to real-world robotics, where door opening is a highly relevant skill for autonomous mobile robots. Door opening is also a well-suited scenario for continual RL, since a robot may encounter many different kinds of doors during its life. The clear separation between different kinds of doors also fits well with the \textit{task-incremental} CL scenario~\citep{threescenarios}, where the task identity is clearly defined, and known at training and evaluation time. Our main contributions are:
\begin{itemize}
    \item A model-free continual RL algorithm, \texttt{HN-PPO}, using hypernetworks to learn a multi-task policy
    \item An evaluation of CL performance in DoorGym using the door opening success rate as the main performance indicator.
\end{itemize}

%\jhOLD{I would use bullet points for the contributions; and if we provide a better evaluation than that might also be a contribution;}

%\saOLD{Right now, the introduction is too short and a few other things need to be mentioned, such as the motivation behind this work (or why this is useful), a brief overview of our experimental setup (why %the doors environment is a good choice), a summary of the main contributions/findings, etc. It is useful for the reader if the doors environment is mentioned here, otherwise it suddenly jumps out of %nothing.

@@

\jhOLD{I don't know if this contradicts what SA and AS but what I would do is to state the area of this work very briefly in the introduction (you are already doing that) and then list the contributions. And then basically start from adam and eve (in terms of RL, but very briefly) i.e. DQN -> Continuous Spaces -> SAC, PPO -> Continual Learning (what is it) -> CL other methods; Mostly you are already doing that. But for example in the paragraph "a varienty of contiual learning".. you describe continual learning more like you would in related work (IMO). 
The reason for that is that the reviewers often do also not know a lot about the very specific field you are working on.
An example of this would be \url{https://arxiv.org/pdf/2206.03787.pdf} -- but this is also a personal taste thing.
SA-CHECK}
\section{Related Work} %\asOLD{Fuse with the previous section and use "Related Work" as its title}
\paragraph{CL strategies} The many strategies for retaining previously learned knowledge, and thus alleviating the catastrophic forgetting problem, can be broadly categorized into four approaches according to \citet{threescenarios2}: Context-specific components, regularization, replay, and template methods. The latter is however most relevant for continual classification problems, and less so for RL settings. A similar classification has also been made in a review of CL methods by \citet{towardsCRL}.\\
Context-specificity methods add parts to the network that are specific for each task, i.e. are only trained on a single task. Such methods include context-specific gating \citep{xdg}, which creates context-specificity by randomly excluding a subset of neurons from the network for each task, or progressive neural networks \citep{pnn}, in which a completely new set of parameters is trained for each task, and information is transferred from previous tasks via lateral connections between layers.\\
Regularization can be applied at two levels to avoid catastrophic forgetting: In \textit{parameter} regularization, the objective is to minimize the changes of parameters which are important for previously learned tasks. The main challenge of parameter regularization is finding which parameters are most important to retain previous knowledge: \citet{ewc} use the Fisher information matrix to estimate parameter importance, and \citet{synapticintelligence} propose an online-learned importance measure in their \textit{Synaptic Intelligence} algorithm. Alternatively, regularization can be applied at the \textit{functional} level. Herein, the output of the network is encouraged to stay close to a target for a set of anchor points. Anchor points could be chosen from previous experience, or if it is undesired to store this data, a knowledge distillation loss can be used for functional regularization, as in \citet{lwf}. They propose a hybrid of functional regularization and parameter storage: \asOLD{ok, and?. Make sure that what you write is informative} Firstly, the network has a context-specific output layer, and regularization is applied between the new and previous outputs of the context-specific components of previous tasks, but using input data from the current task.\\
Finally, replay methods store experience from previous tasks in a buffer, and agents consequently revisit the recorded experience when training for new tasks. The policy is then jointly optimized on the current and replayed experience. Even though conceptually simple, replay suffers from bad scalability over many tasks, since large amounts of memory are required to store all past experience. An approach to improve scalability is to train a generative model alongside the policy model, and then sample from this model to obtain pseudo-data to revisit \citep{generativeReplay}.

\saOLD{I'm not sure we need to write about LwF. But in any case, it will be beneficial to include an overview of continual RL methods (or those specifically applied to robotics). Check this paper for a review of such methods: \url{https://arxiv.org/pdf/2012.13490.pdf}. I also think that we need a little more content here.}

\paragraph{DoorGym} %\asOLD{Again???. As before, fuse with previous section}
The DoorGym environment \citep{doorgym} is a robot simulation based on OpenAI Gym \citep{gym}, where robot arms aim to open a door. Robots are controlled via a set of continuous input variables modeling joint torque (or torque and force on the end effector in case of \texttt{floating} robots). Different types of tasks are modeled through the door knob style (\texttt{pull}, \texttt{lever} or \texttt{round}) as well as the location of the hinge (\texttt{right} or \texttt{left}) and the opening direction (\texttt{pull} or \texttt{push}). Environments within a task domain have a multitude of randomized features, such as the location of the handle on the door, the exact shape of the handle, or the spring force on the lever and hinge.
The original authors of the DoorGym environment \citep{doorgym} provide a baseline PPO and SAC agent for the \texttt{pull} and \texttt{lever} doors. It is demonstrated that PPO and SAC are in principle able to solve the door opening tasks, both in their ground configuration, and with added noise. We use their set of hyperparameters for the PPO agent for our experiments using PPO, as well as as a starting point for finding hyperparameters for HN-PPO. Of note, the authors did not make any attempt at a continual RL agent, nor was the DoorGym environment designed specifically for continual learning.\\
%\citet{MBRLHypernetworks} explore continual RL in DoorGym using the model-based cross-entropy method (CEM) \citep{rubinstein1997optimization} \textit{HyperCRL} on the DoorGym environment. Herein, it is shown that catastrophic forgetting occurs between different DoorGym tasks with traditional RL methods, and task-conditioned hypernetworks are established as a promising method to alleviate this. However, in their paper, it was not shown that the tasks could be completely solved, as they only reported normalized episode rewards, not success rates.
%\sa{fixed missing reference and incorrect text}.
%SA start
\citet{MBRLHypernetworks} propose \textit{HyperCRL}, a model-based continual RL algorithm based on the cross-entropy method (CEM) \citep{rubinstein1997optimization} and hypernetworks \citep{CLHypernetworks}, and evaluate it on the DoorGym environment. Herein, it is shown that catastrophic forgetting occurs between different DoorGym tasks with traditional RL methods, and task-conditioned hypernetworks are established as a promising method to alleviate this. However, their paper does not show if the tasks can be completely solved, as they only report normalized episode rewards, not success rates.
%SA end

\section{Background}
\asOLD{There should be here an introductory sentence on the areas you are going to review below and why. There has to be a link between them.}
Our proposed method uses PPO \citep{ppo} to continually learn policies for different door-opening tasks of the DoorGym environment \citep{doorgym}. A hypernetwork \citep{CLHypernetworks} architecture is used to prevent catastrophic forgetting.

@@

To preserve previously learned skills, regularization is applied at the meta-level: At the beginning of training a new task, the outputs $\Theta_t$ of the hypernetwork are recorded for each previous task embedding $t$ \citep{CLHypernetworks}. Since this output completely defines the target network for a each task, keeping the $\Theta_t$ constant during training of a new task will guarantee preservation of the learned dynamics. We hence apply an L2 penalty on changes of the hypernetwork's output:

@@

Because the update routine requires passing all previous task embeddings through the hypernetwork to calculate the $\Theta_{t,new}$, the computational expense of a training step increases $\mathcal{O}(n)$ with respect to the number of tasks. Importantly though, the model size stays almost constant: only a low-dimensional task embedding vector is added for each new task. This fulfills the CL desideratum of not explicitly accumulating previous experience.

\paragraph{Proximal Policy Optimization}
PPO is a policy gradient method using a \textit{clipped surrogate objective}. A policy is optimized by estimating its gradient, and conducting gradient ascent steps to maximize the reward. The gradient is estimated by differentiating the objective function
\begin{equation}
    L_t(\theta) = \mathbb{E}_t\left[\frac{\pi_\theta(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)}\hat{A}_t\right]
\end{equation}
with advantage $\hat{A}_t$, and a probabilistic policy $\pi_{\theta}(a_t|s_t)$. In PPO, this objective is constrained by clipping excessively large changes in probability ratio \citep{ppo}:
\begin{equation}
\label{ppo-clip}
    L^{clip}_t(\theta)  = \mathbb{E}_t \left[min\left(\frac{\pi_\theta(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)}\hat{A}_t, clip\left(\frac{\pi_\theta(a_t|s_t)}{\pi_{\theta_{old}}(a_t|s_t)}, 1+\epsilon,1-\epsilon \right)\hat{A}_t\right)\right] 
\end{equation}
$\epsilon$ is a hyperparameter and defines the allowable change of the policy. 
%\asOLD{There are some parameters still not defined, like $\pi_\theta$, make sure they all clear what they are}. 
This improves the policy stability by removing big changes in the probability ratios of the old and new policies during a training step. It is conceptually similar to Trust-Region Policy Optimization \citep{trpo}, but is easier to implement, since it omits the KL-divergence based constraint used in Trust-Region Policy Optimization \asOLD{I think you are abusing the use of acronyms, if you plan to use them less than 5 times, do not use the acronym}.

Additionally to the action objective in Eq. \ref{ppo-clip}, we use a trainable value estimator (called a ``critic network") as proposed by \citet{gae} to introduce a value loss term $L^{vf}$. An entropy bonus $S$ is also added to incentivize exploration of the parameter space. The complete objective function thus has 3 parts, with value coefficient $c_v$ and entropy coefficient $c_e$ being hyperparameters.
\begin{equation}
\label{ppo-actorcritic}
    L^{total}_t(\theta) = L^{clip}_t(\theta)+ c_vL^{vf}_t(\theta)+c_eS_{\pi_\theta}(s_t)
\end{equation}

\section{Method}
We extend the existing implementation of PPO in DoorGym to use a hypernetwork to generate the weights of the policy network. Two variants of \texttt{HN-PPO} were implemented: A straightforward implementation (\texttt{HN-PPO}) which places both the actor and critic networks' parameters under the control of the hypernetwork, and a modified variant that only generates the actor network via a hypernetwork and uses an ordinary MLP as the critic (\texttt{HN-PPO+fc}). In the latter variant, the critic is re-initialized for each new task seen by the agent (cf. Appendix \ref{chap:architecture} for details). Since the critic is only used during training, it does not influence the policy at evaluation time, nor is it strictly required to remember multiple dynamics. However, similarity between tasks could allow for forward transfer and benefit learning of new tasks in case of the \texttt{HN-PPO} as the critic is "pre-trained".
The PyTorch hypernetwork implementation used in our experiments is from \cite{auddyHollensteinClfd} and was used without modifications.

\subsection{Environment \asOLD{I think what you wrote about DoorGym should go here, otherwise it is way too many places.}}
\saOLD{Add a subsection for the RL environment and describe here the details of the RL setup and tasks, including any modifications that you made to the default door-gym and the reasons for such modifications. This needs to be connected to the content about door-gym in the background section. So, in the background, you can describe the default door-gym environment and in this section you can describe your specific tasks and modifications.}
In our experiments, we used an unmodified DoorGym \citep{doorgym} environment with the \texttt{blue-floatinghook} robot. This robot type was chosen due to both its simplicity and the good baseline performance on \texttt{pull} and \texttt{lever} doors. The robot resembles a hand with a hook for fingers, and is freely floating in 3D space. It has a 6D continuous input space, with three inputs controlling force in x/y/z direction, and three inputs controlling yaw/pitch/roll torque. None of the noise or vision features of DoorGym were used in our setup, i.e. observations are noise-free and directly derived from the environment simulation. We use the same 6-task sequence laid out in Table~\ref{tab:tasksequence} for all continual learning experiments. CL agents were sequentially trained on each environment. %Figure~\ref{fig:door-examples} provides example images of the robot interacting with some of the door environments.
\saOLD{Some example images would be nice to have.}

\begin{table}[b]
\caption{Series of door opening tasks for CL.}
\label{tab:tasksequence}
\begin{center}
\begin{tabular}{@{}llrr@{}}
\toprule
Task ID & Handle & Hinge location & Opening direction \\ 
\midrule
0 & \texttt{pull}  & right & pull \\
1 & \texttt{pull}  & left  & pull \\
2 & \texttt{lever} & right & pull \\
3 & \texttt{lever} & left  & pull \\
4 & \texttt{lever} & right & push \\
5 & \texttt{lever} & left  & push \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
